Supplementary Material for Food-web complexity alters the fitness landscape

### 2018-06-21 supp_mat_complexity_selection.Rmd
made .Rmd file knits .html efficiently
Former-commit-id: 87e02b4ec2fab993512768bd52398af43e95118e

---
title: "Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore"
author: Matt Barbour
output: html_notebook
---

Load dataset. This dataset is a subset that only includes larva that survive to pupation or turned into parasitoids. We omitted any data where larva mortality was unclear. This enabled us to focus on the selection pressures imposed by insect parasitoids rather than other sources.
```{r setup}
knitr::opts_chunk$set(include = FALSE)

@@

```{r AIC Model Selection, cache=TRUE}

@@

```{r GLMM Univariate Landscapes, eval=FALSE}

@@

```{r GLMM Multivariate Landscapes, eval=FALSE}

@@

```{r AIC Model Selection v0.1, eval=FALSE}

@@

Permutation: qualtiative results are consistent with parametric bootstrapping. Exceptions include: in the simple food-web, there is no evidence of non-linear selection for gall density or gall individuals. In the complex food-web, there is only marginal evidence for non-linear selection acting on gall size, but there is evidence for correlational selection between gall size and the number of individuals per gall.
```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE, eval=FALSE}

@@

```{r Selection Gradients - Bootstrapped Intervals, eval=FALSE}

@@

Compare bootstrapped replicates across treatments, rather than comparing to zero.
```{r Compare bootstrapped replicates across treatments, eval=FALSE}
bootstrap_df %>%
  filter(Phenotype == "Gall size", Selection_Type == "Beta") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)

@@

Now we plot the fitness landscapes associated with different combinations of gall phenotypes. We restrict these plots to 1 SD above and below the mean trait value, as this contains the majority of phenotypes under selection. Therefore, this fitness landscape integrates information from the fitness function with information about distributions of phenotype, and has been suggested to be a more informative way to visualize the magnitude of natural selection.
```{r Fitness Landscapes, eval=FALSE}

>>>>

---
title: Supplementary Material for Food-web complexity alters the fitness landscape
  of an insect herbivore
author: "Matt Barbour"
output:
  html_document: default
  html_notebook: default
---

Load dataset. This dataset is a subset that only includes larva that survive to pupation or turned into parasitoids. We omitted any data where larva mortality was unclear. This enabled us to focus on the selection pressures imposed by insect parasitoids rather than other sources.
```{r setup, include=FALSE}

@@

```{r AIC Model Selection, echo=TRUE, cache=TRUE}

@@

```{r GLMM Univariate Landscapes, eval=FALSE, include=FALSE}

@@

```{r GLMM Multivariate Landscapes, eval=FALSE, include=FALSE}

@@

```{r AIC Model Selection v0.1, eval=FALSE, include=FALSE}

@@

Permutation: qualtiative results are consistent with parametric bootstrapping. Exceptions include: in the simple food-web, there is no evidence of non-linear selection for gall density or gall individuals. In the complex food-web, there is only marginal evidence for non-linear selection acting on gall size, but there is evidence for correlational selection between gall size and the number of individuals per gall.
```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE, eval=FALSE, include=FALSE}

@@

```{r Selection Gradients - Bootstrapped Intervals, eval=FALSE, include=FALSE}

@@

Compare bootstrapped replicates across treatments, rather than comparing to zero.
```{r Compare bootstrapped replicates across treatments, eval=FALSE, include=FALSE}
bootstrap_df %>%
  filter(Phenotype == "Gall size", Selection_Type == "Beta") %>%
  mutate(ID = rep(1:1000,2)) %>%
  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
  mutate(diff_gradient = Complex - Simple) %>%
  summarise(p_value = sum(diff_gradient < 0)/1000)

@@

Now we plot the fitness landscapes associated with different combinations of gall phenotypes. We restrict these plots to 1 SD above and below the mean trait value, as this contains the majority of phenotypes under selection. Therefore, this fitness landscape integrates information from the fitness function with information about distributions of phenotype, and has been suggested to be a more informative way to visualize the magnitude of natural selection.
```{r Fitness Landscapes, eval=FALSE, include=FALSE}
